Synpotic Soil Characterization

### 2025-02-21 3-reports/manuscript_figures.Rmd
update figures

```{r map-poster, fig.height = 9.5, fig.width = 13}

@@

```{r pca_gg, fig.width=10, fig.height=6}
## PCA plots overall
#gg_pca_overall = 
ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1,
         groups = as.character(pca_overall$grp$region), 
         ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_overall$grp$region,
                 fill = groups))+ 
  scale_color_manual(values = c("#16879C", "#BB281E"))+
  scale_fill_manual(values = c("#16879C", "#BB281E"))+
  scale_shape_manual(values = c(23, 21))+
  labs(shape="",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  guides(fill = "none")+
  NULL

@@

### Clustering

```{r cluster_gg}
df_cl %>%
  ggplot(aes(y = cluster, x = site))+
  geom_point(aes(color = transect, shape = transect),
             size = 4, stroke = 1,
             position = position_jitterdodge(jitter.width = 0.0, jitter.height = 0.1, 
                                             dodge.width = 0.4))+
  scale_color_manual(values = pal_transect)

@@

### Normalized values - v1

```{r scaled_gg1, fig.height = 8, fig.width = 7}
data_long = 
  data_combined_wide %>% 
  rename(Cl = Chloride,
         SO4 = Sulfate) %>% 
  pivot_longer(cols = -c(sample_label, region, site, transect, tree_number, horizon)) %>% 
  filter(!is.na(value))

@@

```{r v2-pca_gg, fig.width=10, fig.height=6}
## PCA plots overall
#gg_pca_overall = 
ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
         groups = as.character(pca_overall$grp$region), 
         ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_overall$grp$region,
                 fill = groups))+ 
  scale_color_manual(values = c("#16879C", "#BB281E"))+
  scale_fill_manual(values = c("#16879C", "#BB281E"))+
  scale_shape_manual(values = c(23, 21))+
  labs(shape="",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  guides(fill = "none")+
  NULL

@@

@@

```{r v2-pca_gg_regions-poster, fig.width=7, fig.height=7}

@@

### Clustering

```{r v2-cluster_gg}
df_cl %>%
  ggplot(aes(y = cluster, x = site))+
  geom_point(aes(color = transect, shape = transect),
             size = 4, stroke = 1,
             position = position_jitterdodge(jitter.width = 0.0, jitter.height = 0.1, 
                                             dodge.width = 0.4))+
  scale_color_manual(values = pal_transect)

@@

### Normalized values - v1

@@

```{r v2-scaled_gg2, fig.height = 8, fig.width = 8}
data_long_all = 
  data_combined_wide %>% 
  dplyr::select(-c(TN, CEC, K, Mg, Sulfate, NO3N, pH, spConductance, SOM, DIC, Al)) %>% 
  pivot_longer(cols = -c(sample_label, region, site, transect, tree_number, horizon)) %>% 
  filter(!is.na(value))

@@

```{r v2-scaled_gg2_split, fig.height = 10, fig.width = 14}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

@@

@@

```{r v2-scaled_gg2_gwi, fig.height = 8, fig.width = 8}
data_scaled_NEW %>% 
  filter(site == "GWI") %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 2)+
  facet_wrap( ~ name )+
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())

@@

```{r analytesx-4, fig.height = 15, fig.width = 8}
cowplot::plot_grid(gg_tc, gg_fe, gg_p, ncol = 1)
```

>>>>

```{r map-poster, fig.height = 9.5, fig.width = 13, eval=FALSE}

@@

```{r cluster_gg, eval=FALSE}
df_cl %>%
  ggplot(aes(y = cluster, x = site))+
  geom_point(aes(color = transect, shape = transect),
             size = 4, stroke = 1,
             position = position_jitterdodge(jitter.width = 0.0, jitter.height = 0.1, 
                                             dodge.width = 0.4))+
  scale_color_manual(values = pal_transect)

```{r pca_gg, fig.width=10, fig.height=6, eval=FALSE}
## PCA plots overall
#gg_pca_overall = 
ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1,
         groups = as.character(pca_overall$grp$region), 
         ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_overall$grp$region,
                 fill = groups))+ 
  scale_color_manual(values = c("#16879C", "#BB281E"))+
  scale_fill_manual(values = c("#16879C", "#BB281E"))+
  scale_shape_manual(values = c(23, 21))+
  labs(shape="",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  guides(fill = "none")+
  NULL

@@

@@

```{r scaled_gg1, fig.height = 8, fig.width = 7, eval=FALSE}
data_long = 
  data_combined_wide %>% 
  rename(Cl = Chloride,
         SO4 = Sulfate) %>% 
  pivot_longer(cols = -c(sample_label, region, site, transect, tree_number, horizon)) %>% 
  filter(!is.na(value))

@@

@@

```{r v2-cluster_gg, include=FALSE}
df_cl %>%
  ggplot(aes(y = cluster, x = site))+
  geom_point(aes(color = transect, shape = transect),
             size = 4, stroke = 1,
             position = position_jitterdodge(jitter.width = 0.0, jitter.height = 0.1, 
                                             dodge.width = 0.4))+
  scale_color_manual(values = pal_transect)

## PCA by region

@@

```{r v2-pca_gg_regions-poster, fig.width=7, fig.height=7, eval=FALSE}

@@

@@

@@

### Normalized values

```{r v2-scaled_gg2, fig.height = 8, fig.width = 8, eval=FALSE}
data_long_all = 
  data_combined_wide %>% 
  dplyr::select(-c(TN, CEC, K, Mg, Sulfate, NO3N, pH, spConductance, SOM, DIC, Al)) %>% 
  pivot_longer(cols = -c(sample_label, region, site, transect, tree_number, horizon)) %>% 
  filter(!is.na(value))

@@

```{r v2-scaled_gg2_split, fig.height = 10, fig.width = 14, eval=FALSE}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

@@

### only select analytes

@@

```{r v2-scaled_gg2_gwi, fig.height = 8, fig.width = 8, eval=FALSE}
data_scaled_NEW %>% 
  filter(site == "GWI") %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 2)+
  facet_wrap( ~ name )+
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())

@@

```{r analytesx-4, fig.height = 15, fig.width = 8, eval=FALSE}
cowplot::plot_grid(gg_tc, gg_fe, gg_p, ncol = 1)
```
